Results

### 2024-04-29 Analysis/04_Summarise_results.Rmd
Update 04_Summarise_results.Rmd

## Empirical
load("../Data/Processed/empirical_data.rda")
empirical_results <- list("empirical" = bkp)
#rm1 = "extant", rm2 = "historic", rm3 = "prehistoric"

#TODO: reorder so to have rm2, rm3, rm1

@@

```{r, fig.width = 8, fig.height = 10, echo = FALSE}
col_vector <- c(rep("blue", 4), # The richness ones
                rep("orange", 7), # The divergence ones
                rep("darkgreen", 4)) # The regularity ones
## The plot
fancy.plot(scaled_results_2d, col = col_vector, lm = model_fits_2d, null = null_differences_2d, metric.names = fancy_names)

## Pdf version
pdf(file = "../Manuscript/Figures/results_per_metric_per_stressor_2d.pdf", height = 9, width = 9)
fancy.plot(scaled_results_2d, col = col_vector, lm = model_fits_2d, null = null_differences_2d, metric.names = fancy_names)
dev.off()
```

@@

```{r}
## The plot
fancy.plot(scaled_results_3d, col = col_vector, lm = model_fits_3d, null = null_differences_3d, metric.names = fancy_names)

## Pdf version
pdf(file = "../Manuscript/Figures/results_per_metric_per_stressor_3d.pdf", height = 9, width = 9)
fancy.plot(scaled_results_3d, col = col_vector, lm = model_fits_3d, null = null_differences_3d, metric.names = fancy_names)
dev.off()
```

```{r}
## The plot
fancy.plot(scaled_results_4d, col = col_vector, lm = model_fits_4d, null = null_differences_4d, metric.names = fancy_names)

## Pdf version
pdf(file = "../Manuscript/Figures/results_per_metric_per_stressor_4d.pdf", height = 9, width = 9)
fancy.plot(scaled_results_4d, col = col_vector, lm = model_fits_4d, null = null_differences_4d, metric.names = fancy_names)
dev.off()
```

```{r}
## The plot
fancy.plot(scaled_results_5d, col = col_vector, lm = model_fits_5d, null = null_differences_5d, metric.names = fancy_names)

## Pdf version
pdf(file = "../Manuscript/Figures/results_per_metric_per_stressor_5d.pdf", height = 9, width = 9)
fancy.plot(scaled_results_5d, col = col_vector, lm = model_fits_5d, null = null_differences_5d, metric.names = fancy_names)
dev.off()
```

```{r}
## The plot
fancy.plot(scaled_results_8d, col = col_vector, lm = model_fits_8d, null = null_differences_8d, metric.names = fancy_names)

## Pdf version
pdf(file = "../Manuscript/Figures/results_per_metric_per_stressor_8d.pdf", height = 9, width = 9)
fancy.plot(scaled_results_8d, col = col_vector, lm = model_fits_8d, null = null_differences_8d, metric.names = fancy_names)
dev.off()
```

@@

## Pdf version
pdf(file = "../Manuscript/Figures/results_per_metric_per_stressor_emp.pdf", height = 9, width = 4)
fancy.plot(scaled_results_emp, col = col_vector, lm = NULL, null = null_differences_emp, metric.names = rev(fancy_names), , pch = c(19,15,17))
dev.off()
```

Figure 3: Empirical data. Plain circles represents the metric for historic data (53 % - 63/118 species), lightly fainted squares for prehistoric data (46% - 55/118 species), and fainted triangles for extant data (31% - 37/118 species).
<!-- TODO: this caption is for the empirical data re-arranged as rm2, rm3, rm1 -->

@@

## Empty plot
plot(NULL, ylim = range(pretty(ylim)), xlim = c(2, 8), ylab = "Time (log(s))", xlab = "dimensions")

@@

## Ti me
axis(4, at = c(1, 4.1, 7, 8.189), labels = c("1 sec", "1 min", "30 min", "1 hour"), las = 2)

>>>>

## Empirical
load("../Data/Processed/empirical_data.rda")
empirical_results <- list("empirical" = bkp)
#rm1 = "extant", rm2 = "historic", rm3 = "prehistoric"
extants <- grep("rm1", colnames(empirical_results$empirical$results_table))
historics <- grep("rm2", colnames(empirical_results$empirical$results_table))
prehistorics <- grep("rm3", colnames(empirical_results$empirical$results_table))
## Reorder by percentage removed (historics > prehistorics > extants)
empirical_results$empirical$results_table <- empirical_results$empirical$results_table[, c(historics, prehistorics, extants)]
```

@@

```{r, fig.width = 8, fig.height = 10, echo = FALSE}
col_vector <- c(rep("blue", 4), # The richness ones
                rep("orange", 7), # The divergence ones
                rep("darkgreen", 4)) # The regularity ones
## The plot
fancy.plot(scaled_results_2d, col = col_vector, lm = model_fits_2d, null = null_differences_2d, metric.names = fancy_names, pch = rep(19,4))

## Pdf version
pdf(file = "../Manuscript/Figures/results_per_metric_per_stressor_2d.pdf", height = 9, width = 9)
fancy.plot(scaled_results_2d, col = col_vector, lm = model_fits_2d, null = null_differences_2d, metric.names = fancy_names, pch = rep(19,4))
dev.off()
```

@@

```{r}
## The plot
fancy.plot(scaled_results_3d, col = col_vector, lm = model_fits_3d, null = null_differences_3d, metric.names = fancy_names, pch = rep(19,4))

## Pdf version
pdf(file = "../Manuscript/Figures/results_per_metric_per_stressor_3d.pdf", height = 9, width = 9)
fancy.plot(scaled_results_3d, col = col_vector, lm = model_fits_3d, null = null_differences_3d, metric.names = fancy_names, pch = rep(19,4))
dev.off()
```

```{r}
## The plot
fancy.plot(scaled_results_4d, col = col_vector, lm = model_fits_4d, null = null_differences_4d, metric.names = fancy_names, pch = rep(19,4))

## Pdf version
pdf(file = "../Manuscript/Figures/results_per_metric_per_stressor_4d.pdf", height = 9, width = 9)
fancy.plot(scaled_results_4d, col = col_vector, lm = model_fits_4d, null = null_differences_4d, metric.names = fancy_names, pch = rep(19,4))
dev.off()
```

```{r}
## The plot
fancy.plot(scaled_results_5d, col = col_vector, lm = model_fits_5d, null = null_differences_5d, metric.names = fancy_names, pch = rep(19,4))

## Pdf version
pdf(file = "../Manuscript/Figures/results_per_metric_per_stressor_5d.pdf", height = 9, width = 9)
fancy.plot(scaled_results_5d, col = col_vector, lm = model_fits_5d, null = null_differences_5d, metric.names = fancy_names, pch = rep(19,4))
dev.off()
```

```{r}
## The plot
fancy.plot(scaled_results_8d, col = col_vector, lm = model_fits_8d, null = null_differences_8d, metric.names = fancy_names, pch = rep(19,4))

## Pdf version
pdf(file = "../Manuscript/Figures/results_per_metric_per_stressor_8d.pdf", height = 9, width = 9)
fancy.plot(scaled_results_8d, col = col_vector, lm = model_fits_8d, null = null_differences_8d, metric.names = fancy_names, pch = rep(19,4))
dev.off()
```

@@

## Pdf version
pdf(file = "../Manuscript/Figures/results_per_metric_per_stressor_emp.pdf", height = 9, width = 4.5)
fancy.plot(scaled_results_emp, col = col_vector, lm = NULL, null = null_differences_emp, metric.names = rev(fancy_names), pch = c(19,15,17))
dev.off()
```

Figure 3: Empirical data. Plain circles represents the metric for historic data (53 % - 63/118 species), lightly fainted squares for prehistoric data (46% - 55/118 species), and fainted triangles for extant data (31% - 37/118 species).

@@

pdf(file = "../Manuscript/Figures/time_per_metric.pdf", height = 6, width = 7)
par(mar =c(5, 4, 4, 4) + 0.1)
## Empty plot
plot(NULL, ylim = range(pretty(ylim)), xlim = c(2, 8), ylab = "Time (log(s))", xlab = "dimensions")
abline(h = c(1, 4.1, 7, 8.189), col = "grey")

@@

## Time
axis(4, at = c(1, 4.1, 7, 8.189), labels = c("1 sec", "1 min", "30 min", "1 hour"), las = 2)
dev.off()
